Using statistics to guide response to the HIV epidemic

### 2023-05-17 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Slides up #144

* In medicine, we want to deliver the right intervention, at the right time
* \textcolor{hilit}{Precision medicine} seeks to do that at the individual-level
* \textcolor{hilit}{Precision public health} seeks to do it at the population-level

@@

## What have we done

@@

```{r echo=FALSE, warning=FALSE, out.width="350px", fig.cap = "Example of model structure: we assume that neighbouring districts are similar."}
areas <- sf::read_sf("depends/zwe_areas.geojson")

@@

* Extension to adults 15-49 and further countries
* Generation of estimates led by country teams as a part of a yearly process: data ownership, data use, and data quality

@@

* Being good (perhaps not great) at a useful enough collection of things
* Feeling like no one care about the application at methods conferences, and no one cares about the methods at application conferences

@@

* A lot of disciplines required: Epidemiology, public health, health economics, behavioural science, implementation science, mathematics, statistics, computer science, software engineering
* Academia pushes against this by wanting every contribution to be marginally interesting in each field

@@

```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website`"}
knitr::include_graphics("blog-post-updated.png")
```

>>>>

* In medicine, we want to deliver the right intervention, at the right time
* \textcolor{hilit}{Precision medicine} seeks to do it at the individual-level
* \textcolor{hilit}{Precision public health} seeks to do it at the population-level

@@

## The work we've done

@@

```{r echo=FALSE, out.width="350px", fig.cap = "Example DHS questionnaire."}
knitr::include_graphics("dhs.png")
```

```{r echo=FALSE, out.width="350px", fig.cap = "How we allocated survey respondents to risk groups based on the questionnaire."}
knitr::include_graphics("depends/category-flowchart.pdf")
```

## What do you mean by model?

* Translation of scientific knowledge into a mathematical \textcolor{hilit}{data generating process}. If we wanted to, we could simulate fake data
* Given observed data, we use Bayes theorem to update our beliefs about the parameters of the model

```{r echo=FALSE, warning=FALSE, out.width="350px", fig.cap = "An example of scientific knowledge included in the model is that we assume that neighbouring districts are similar. This is Tobler's first law of geography. The pictured country is Tanzania."}
areas <- sf::read_sf("depends/tza_areas.geojson")

@@

* Extension to adults 15-49 and further countries
* Generation of estimates led by country teams as a part of a yearly process
* Virtuous cycle of data \textcolor{hilit}{ownership}, data \textcolor{hilit}{use}, and data \textcolor{hilit}{quality}

@@

* Being good (perhaps not great) at a useful enough collection of things
* Feeling like no one cares about the application at methods conferences, and no one cares about the methods at application conferences

@@

* A lot of disciplines required: Epidemiology, public health, health economics, behavioural science, implementation science, mathematics, statistics, computer science, software engineering
* Academia pushes against this by wanting every contribution to be marginally interesting in each field
* MRC GIDA at Imperial does a good job here, in my opinion

@@

```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website."}
knitr::include_graphics("blog-post-updated.png")
```
